Scottish Child Payment Interventions

### 2024-01-22 minos/outcomes/CPR_vis.Rmd
Further speed improvements to data reading functions using fread function from data.table. Also changed submission scripts to request a full node

---
title: "Child Poverty Reduction Interventions"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

```{r read_data}
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'scaled_scotland')
out.path <- here::here('output', 'default_config_batch')

# define subset of variables to reduce size of batch output
var.list <- c('pidp', 'hidp', 'time', 'weight', 
              'age', 'ethnicity', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
              'hh_income', 'child_ages', 'simd_decile',
              'SF_12', 'matdep_child')

@@

### NOTE: READING INTERVENTION OUTPUTS IS CURRENTLY BROKEN FOR BATCH RUNS
#         THIS IS BECAUSE WE ARE NO LONGER USING BOOST_AMOUNT

>>>>

---
title: "Child Poverty Reduction Interventions"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console #inline
---

@@

```{r read_data}
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
out.path <- here::here('output', 'scaled_scotland')
#out.path <- here::here('output', 'default_config_batch')
out.path <- here::here('output', 'default_config_batch2')

# define subset of variables to reduce size of batch output
var.list <- c('pidp', 'hidp', 'time', 'weight', 
              'age', 'ethnicity', 'region', 'nkids', 'nkids_ind', 'S7_labour_state',
              'hh_income', 'child_ages', #'simd_decile',
              'SF_12', 'matdep_child')

@@

### 2024-01-22 minos/outcomes/SCP_vis.Rmd
Further speed improvements to data reading functions using fread function from data.table. Also changed submission scripts to request a full node

---
title: "Scottish Child Payment Interventions"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)
require(dplyr)
require(tidyr)
require(purrr)
require(parallel)

@@

```{r read_data}
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'scaled_scotland')
#out.path <- here::here('output', 'default_config_batch')
out.path <- here::here('output', 'scaled_scotland_batch')
#out.path <- here::here('output', 'scaled_scotland_small')

@@

base <- read_output(out.path, 
                    scenario = 'baseline', 
                    var.list = var.list,
                    verbose = TRUE)
int25 <- read_output(out.path, 
                      scenario = '25UniversalCredit', 
                      var.list = var.list,
                      verbose = TRUE)
# int30 <- read_output(out.path,
#                       scenario = '30UniversalCredit',
#                       var.list = var.list,
#                       verbose = TRUE)
# int35 <- read_output(out.path,
#                       scenario = '35UniversalCredit',
#                       var.list = var.list,
#                       verbose = TRUE)
# int40 <- read_output(out.path,
#                       scenario = '40UniversalCredit',
#                       var.list = var.list,
#                       verbose = TRUE)
# int45 <- read_output(out.path,
#                       scenario = '45UniversalCredit',
#                       var.list = var.list,
#                       verbose = TRUE)
int50 <- read_output(out.path,
                      scenario = '50UniversalCredit',
                      var.list = var.list,
                      verbose = TRUE)

#int.list <- c(int25, int30, int35, int40, int45, int50)
# int.list <- list(base, int25, int30, int35, int40, int45, int50)
# scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')

int.list <- list(base, int25, int50)
scen.list <- c('base', 'int25', 'int50')

>>>>

---
title: "Scottish Child Payment Interventions"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console #inline
---

@@

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)
require(dplyr)
require(tidyr)
require(purrr)
require(parallel)
require(data.table)

@@

```{r read_data}
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
out.path <- here::here('output', 'scaled_scotland')
#out.path <- here::here('output', 'default_config_batch')
#out.path <- here::here('output', 'scaled_scotland_batch')
#out.path <- here::here('output', 'scaled_scotland_small')
#out.path <- here::here('output', 'tmp_default_baseline')

@@

base <- read_output(out.path, 
                    scenario = 'baseline', 
                    var.list = var.list,
                    verbose = TRUE)
int25 <- read_output(out.path,
                      scenario = '25UniversalCredit',
                      var.list = var.list,
                      verbose = TRUE)
int30 <- read_output(out.path,
                      scenario = '30UniversalCredit',
                      var.list = var.list,
                      verbose = TRUE)
int35 <- read_output(out.path,
                      scenario = '35UniversalCredit',
                      var.list = var.list,
                      verbose = TRUE)
int40 <- read_output(out.path,
                      scenario = '40UniversalCredit',
                      var.list = var.list,
                      verbose = TRUE)
int45 <- read_output(out.path,
                      scenario = '45UniversalCredit',
                      var.list = var.list,
                      verbose = TRUE)
int50 <- read_output(out.path,
                      scenario = '50UniversalCredit',
                      var.list = var.list,
                      verbose = TRUE)

#int.list <- c(int25, int30, int35, int40, int45, int50)
int.list <- list(base, int25, int30, int35, int40, int45, int50)
scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')

# int.list <- list(base, int25, int50)
# scen.list <- c('base', 'int25', 'int50')
